```{r echo=FALSE}
knitr::opts_chunk$set(comment=NA)
```

# Targeting and Retaining Customers

## R Packages and Datasets for Topic 4

``` {r t4packagesdata, message=FALSE}
library(ggplot2)       # Advanced graphing capabilities
library(tidyr)         # Easier programming 
library(GGally)        # Scatterplot matrix
library(flextable)     # Better HTML Tables
library(htmlTable)     # Better HTML Tables
library(jtools)        # Concise regression results
library(huxtable)      # Nice tables using jtools
library(dplyr)         # Easier programming
library(caret)         # Create data partitions
library(cowplot)
load("Topic04/bankmktg.rdata")
load("Topic04/telecom.rdata")
```

## Targeting Customers

* One-to-One Marketing
    * Time consuming
    * Costly
* Mass Marketing
    * Customer needs not being met
* Target Marketing
    * Market to those likely to...

### Goal

Target customers with the highest likelihood of a favorable outcome using explanatory variables

* Outcome variable could be:
    * Purchase
    * Sales
    * Costs
    * Profitability
    * CLV
* Explanatory variables could be:
    * Demographics
    * Behaviors
    * Usage
    * Lifestyles
    
The outcome variable will dictate the type of analysis we can perform

* Continuous outcome variables have a meaningful magnitude
    * Use linear regression
* Categorical outcome variables do not have a meaningful magnitude
    * Use logistic regression
    
## Retaining Customers

Importance of retention:

> Reducing defections $5\%$ boosts profits $25\%$ to $85\%$.  — Frederick F. Reichheld and W. Earl Sasser, Jr.

### Goal

Identify factors (i.e., independent variables) that increase the likelihood of retention (or decrease the likelihood of churn)

* Retention (or Churn) is the outcome or dependent variable
    * DV = Binary, so Method = Logistic Regression
    
## Targeting Customers (Linear Regression) Example

### Overview

* Customer revenue, usage, and demographics for a cell phone provider
* DV:
    * Mean monthly revenue (prior 6 months), `avg6rev`
* IVs:
    * Mean monthly minutes (prior 6 months), `avg6mou`
    * Mean monthly customer care calls, `cc`
    * Mean monthly directory assistance calls, `da`
    * Mean monthly overage minutes, `ovrmou`
    * Household income (dollars), `income`
    * Own home (Yes; No), `own`
    
### Summarize Data

* Useful to examine data prior to specifying the model
    * Summary Statistics
    <caption>(\#tab:t4summstat01) Summary Statistics ([R code](#table-reftabt4summstat01))</caption>
    ``` {r t4summstat01, echo=FALSE}
    summary(telecom)
    ```

    * Scatterplot Matrix (with Correlations)
    ```{r t4scatmat01, echo=FALSE, fig.cap="Scatterplot Matrix with Correlations ([R code](#figure-reffigt4scatmat01))", message=FALSE, cache=TRUE}
    ggpairs(telecom[,1:6],  # Select first 6 columns of data set
            lower=list(continuous=
                      wrap("smooth", method="lm", se=FALSE, # Add fit line
                           color="midnightblue")),  # Set dot color
            diag=list(continuous="blankDiag"))  # Set diagonals to be blank
    ```

### Model Specification

* Goal: Determine what behaviors and demographics are associated with high revenue customers
* IVs are expected to be ones that are related to revenue
* Model: $avg6rev=\alpha+\beta_1avg6mou+\beta_2cc+\beta_3da+\beta_4ovrmou+\beta_5income+\beta_6own$

### Model Interpretation

#### Results

<caption>(\#tab:t4lr01) Linear Regression Results ([R code](#table-reftabt4lr01))</caption>
```{r t4lr01, echo=FALSE, cache=TRUE}
target <- lm(avg6rev ~ avg6mou + cc + da + ovrmou + income + own,
             data=telecom)
summary(target)

```
$avg6rev=31.593+.049avg6mou-1.279cc+1.814da+.178ovrmou-.014income-4.081own$

#### Testing Overall Model Significance

* Relationship between DV and combined effects of IVs
* $H_0: \text{all }\beta_k=0$ vs. $H_a: \text{at least one }\beta_k\ne0$
* Use F-statistic to test
* Conclusion:  With a F-statistic of $921.4$ and a $p<.001$, we conclude that at least one $\beta_k$ is significant

#### Assessing overall model fit

* How much variation in the DV is explained by the model
* Use $R^2$ to assess
* Use Adjusted $R^2$ to compare models
* Conclusion: Based on the $R^2$, about $70\%$ of the variance in `avg6rev` is explained by the model

#### Interpret Individual IVs

* Relationship between DV and each IV
* $H_0: \beta_k=0$ vs. $H_a: \beta_k\ne0$
* Interpret significant relationships
    * `avg6mou`
        * With $p<.001$, `avg6mou` has a significant effect on `avg6rev`.
        * A one unit increase in `avg6mou` is predicted to increase `avg6rev` by $.049$ units.
    * `cc`
        * With $p<.001$, `cc` has a significant effect on `avg6rev`.
        * A one unit increase in `cc` is predicted to decrease `avg6rev` by $1.279$ units.
    * `da`
        * With $p<.001$, `da` has a significant effect on `avg6rev`.
        * A one unit increase in `da` is predicted to increase `avg6rev` by $1.814$ units.
    * `ovrmou`
        * With $p<.001$, `ovrmou` has a significant effect on `avg6rev`.
        * A one unit increase in `ovrmou` is predicted to increase `avg6rev` by $.017$ units.
    * `own`
        * With $p<.001$, `own` has a significant effect on `avg6rev`.
        * Those that own their home have $4.081$ units less revenue per month than those that do not.
* A standardized $\beta$ is the effect of a single standard deviation change in the IV on the DV
    * Higher absolute values are more important
    * Conclusion: `avg6mou` is the biggest driver of avg6rev

    <caption>(\#tab:t4stdbeta1) Standardized Beta Coefficients ([R code](#table-reftabt4stdbeta1))</caption>
    ```{r t4lrstdbeta1, echo=FALSE}
    # Use user-defined function 'lm_beta.R'
    source("Topic02/lm_beta.R")
    htmlTable(lm_beta(target, digits=4))
    ```

* Sometimes helps to visually examine the IVs for interpretation
* Plots show predicted DV at different levels of significant IVs 

    ```{r t4marginplots01, echo=FALSE}
    # Calculate mean values for continuous variables
    av6mou <- mean(telecom$avg6mou)
    cc <- mean(telecom$cc)
    da <- mean(telecom$da)
    ovrmou <- mean(telecom$ovrmou)
    income <- mean(telecom$income)
    # Create dataframe for prediction at different levels of 'avg6mou'
    a6m.pred <- crossing(avg6mou=seq(0,700,50), # 15 levels
                         cc=cc, da=da, ovrmou=ovrmou, income=income,
                         own=c("Yes","No"))
    # Append linear prediction and confidence intervals to new data frame
    a6m.pred$p <- as.data.frame(
       predict.lm(target, 
                  a6m.pred,
                  interval="confidence")
    )
    ```
       



## R Code

### Figure \@ref(fig:t4scatmat01) {.unlisted .unnumbered}

```{r t4scatmat01code, eval=FALSE}
ggpairs(telecom[,1:6],  # Select first 6 columns of data set
        lower=list(continuous=
                   wrap("smooth", method="lm", se=FALSE, # Add fit line
                        color="midnightblue")),  # Set dot color
        diag=list(continuous="blankDiag"))  # Set diagonals to be blank
```   

### Table \@ref(tab:t4summstat01) {.unlisted .unnumbered}

``` {r t4summstat01code, eval=FALSE}
summary(telecom)
```

### Table \@ref(tab:t4lr01) {.unlisted .unnumbered}

```{r t4lr01code, eval=FALSE}
target <- lm(avg6rev ~ avg6mou + cc + da + ovrmou + income + own,
             data=telecom)
summary(target)

```

### Table \@ref(tab:t4stdbeta11) {.unlisted .unnumbered}

    ```{r t4lrstdbeta1code, eval=FALSE}
    # Use user-defined function 'lm_beta.R'
    source("Topic02/lm_beta.R")
    htmlTable(lm_beta(target, digits=4))
    ```

