```{r echo=FALSE}
knitr::opts_chunk$set(comment=NA)
options(scipen=5)  # Turns off scientific notation
```

# Conjoint Analysis

## R Packages and Datasets for Topic 8

``` {r t8packagesdata, message=FALSE}
library(ggplot2)       # Advanced graphing capabilities
library(dplyr)         # Easier programming
load("Topic08/airlineca.rdata")
```
``` {r t8packagesdata2, echo=FALSE, message=FALSE}
library(flextable)
library(kableExtra)
```

## Why Conjoint?

### Buyers versus Sellers

* Buyers want to *Maximize Utility*
    * Most desirable features
    * Lowest possible price
* Sellers want to *Maximize Profits*
    * Lower costs
    * Greater value
    
### Breaking Down Products

* Buyers value products based on the sum of their parts
    * If we can learn how buyers value components, we can design better positioned products, and improve profitability
    
### Learning What Customers Want

* Ask direct questions about preference
    * Unfortunately, responses are often unenlightening
    * No information about sensitivities within ranges
* Ask direct questions about importance
    * Typically results if everything being important
    * Problem of low discrimination
    
### How is Conjoint Analysis Different?

* Present consumers with realistic tradeoffs
    * For example: ***Which would you prefer in your next automobile?***
        a) 210 Horsepower, 18 MPG
        b) 140 Horsepower, 28 MPG
    * If "a" is selected, we infer that they prefer power
    * If "b" is selected, we infer that they prefer fuel economy
* Doesn't ask directly about preferences or importance
    * Preferences and importance inferred from tradeoffs made

### Why Does Conjoint Analysis Work?

* Consumers:
    * Make tradeoffs similar to those in the real market
    * Are discouraged from saying all features are equally desirable
    * Must make difficult tradeoffs, which provides more valuable info
    
### Practical Guidelines

* Should be able to specify product as a bundle of attributes  
* Need to know the determinant attributes
* Respondents should be familiar with category and attributes
* Firm should be able to act on results

## How Conjoint Analysis Works

1) Break down product into component parts or features
2) Vary features to “build” many product concepts
3) Ask respondents to rank/rate or choose between concepts
4) Use statistics to derive each feature’s unique value  $\leftarrow$ Marketing analytics

### Rules for Creating the Attribute List

* Each attribute has varying levels
    * EXAMPLE
        * **Attribute**: Brand<br>*Levels*: Apple; Samsung; Moto
        * **Attribute**: Screen Size<br>*Levels*: 5"; 5.5"; 6"
        * **Attribute**: Battery<br>*Levels*: 12 hrs.; 18 hrs.; 24 hrs.
        * **Attribute**: Price<br>*Levels*: \$400; \$700; \$1000
        * **Attribute**: Storage<br>*Levels*: 32GB; 64GB; 128GB
* Try to balance number of levels across attributes
    * Reduces the number of levels bias: Holding all else constant, attributes with more levels than others will be biased upwards in importance
    * EXAMPLE
        * A PRICE attribute with levels of \$10, \$12, \$14,\$16, \$18, \$20 will have a higher relative importance compared to other attributes than if the PRICE attribute levels were \$10, \$15, \$20
* Attribute levels should be mutually exclusive
    * EXAMPLE
        * **Attribute**: Accessories<br>*Levels*: Screen protector; Phone case; Protection plan
        * We could not determine the value of providing these features at the same time
        
### Build Concepts

* Suppose three attributes, each with three levels
    * There would be $3\times 3\times 3=27$ different profiles
    
### Rate/Rank/Choose Concepts

* EXAMPLE
    * **Rate**: On a scale of 1 to 100, how likely would you be to purchase the following product combination?
    * **Rank**: Please rate the following combinations from most likely to least likely to purchase.
    * **Choose**: Which of the following product combinations would you choose?
* Traditional Conjoint
    * Rate or rank profiles
    * Good for small number of attributes
    * Can work for small samples
* Adaptive Conjoint
    * Rate attributes and choose profiles
    * Good for high number of attributes
    * Bad for pricing research
* Choice-Based Conjoint
    * Choose profiles
    * Best mirrors real-world purchase
    * Requires larger sample sizes
    
### Use Statistics to Derive Unique Value

* Traditional Conjoint
    * Uses regression-based methods
* Adaptive Conjoint
    * Use hierarchical Bayesian methods
* Choice-Based Conjoint
    * Uses multinomial choice models with hierarchical Bayesian methods
* QUESTION: What type of data output do we get from conjoint analysis?<BR>
ANSWER: Part-worth utilities
    * Numerical values that	reflect how desirable different features are
        * How consumers value each level of each attribute
    * Can be created for each respondent
    
## Part-Worth Utilities and Importances

### Characteristics of Part-Worth Utilities

* EXAMPLE:
    * Suppose we studied burritos and used two attributes: *Price* and *Meat*
    * We might end up with the following part-worth utilities for a single respondent
    
    ```{r, echo=FALSE, message=FALSE, warning=FALSE}
    Level <- c("$6", "$8", "$10")
    Utility <- c(48,32,24)
    df <- data.frame(cbind(Level, Utility))
    kable(df, format="html") %>% 
      kable_styling("striped", full_width=FALSE) %>% 
      add_header_above(c("Price"=2))
    
    Level <- c("Chicken", "Steak")
    Utility <- c(29,13)
    df <- data.frame(cbind(Level, Utility))
    kable(df, format="html") %>% 
      kable_styling("striped", full_width=FALSE) %>% 
      add_header_above(c("Meat"=2))
    ```

* Higher is more preferred
    * EXAMPLE:
        * \$6 preferred to \$8
        * \$8 preferred to \$10
        * Chicken preferred to Steak
* Can be positive or negative
    * Higher is still more preferred
* Estimated on an interval scale
    * Addition/subtraction allowed
    * Multiplication/division not allowed
    * EXAMPLE: 
        * Can't say \$6 is "twice as preferred" as \$10
* CANNOT compare level from one attribute with level from another attribute
    * EXAMPLE:
        * Can’t say \$6 is more preferred than Chicken
* CAN compare differences between levels of one attribute with levels of another attribute
    * EXAMPLE: 
        * Preference difference between \$6 and \$8 is same as between Chicken and Steak
* Total utility for a profile is additive
    * EXAMPLE: 
        * $3\times 2=6$ product combinations with the following utilities:
            * \$6	–	Chicken: 48 + 29 = 77
            * \$8	–	Chicken: 32 + 29 = 61
            * \$6	–	Steak: 48 + 13 = 61
            * \$10 –	Chicken: 24 + 29 = 53
            * \$8	–	Steak: 32 + 13 = 45
            * \$10	–	Steak: 24 + 13 = 37
            
### Calculating Part-Worth Utilities (traditional conjoint)

* Each respondent provided ratings on many product profiles
* For each respondent, run a linear regression:
    * $profilerating_i=\alpha+\beta_kattr_{ik}$
* Works if: profiles rated > attribute levels in the regression equation
* Regression coefficients become the part-worth utilities
    * Not concerned with significance

### From Utilities to Importances

* Part-worth utilities
    * DO… directly provide a measure of preference within attributes
    * DON’T… directly provide a measure of each attributes importance
* Conjoint Importances
    * Measures how much influence each attribute has on choice
    * Considers the difference each attribute could make in total utility

### Calculating Conjoint Importances

1) Calculate utility range for each attribute
2) Sum up ranges
3) Calculate percent of "total range" each attribute contributes

* EXAMPLE:
    * Suppose we add a third attribute to our burrito example: *Guacamole*
    * We might end up with the following part-worth utilities for a single respondent
    
    ```{r, echo=FALSE, message=FALSE, warning=FALSE}
    Level <- c("$6", "$8", "$10")
    Utility <- c(48,32,24)
    df <- data.frame(cbind(Level, Utility))
    kable(df, format="html") %>% 
      kable_styling("striped", full_width=FALSE) %>% 
      add_header_above(c("Price"=2))
    
    Level <- c("Chicken", "Steak")
    Utility <- c(29,13)
    df <- data.frame(cbind(Level, Utility))
    kable(df, format="html") %>% 
      kable_styling("striped", full_width=FALSE) %>% 
      add_header_above(c("Meat"=2))
    
    Level <- c("Yes", "No")
    Utility <- c(47,15)
    df <- data.frame(cbind(Level, Utility))
    kable(df, format="html") %>% 
      kable_styling("striped", full_width=FALSE) %>% 
      add_header_above(c("Guacamole"=2))
    ```

    * Step 1: Calculate range for each attirbute
        * **Price**: \$6 (high) - \$10 (low) = 48 - 24 = 24
        * **Meat**: Chicken (high) - Steak (low) = 29 - 13 = 16
        * **Guacamole**: Yes (high) - No (low) = 47 - 15 = 24
    * Step 2: Sum up the ranges
        * 24 + 16 + 32 = 72
    * Step 3: Calculate percent of "total range" each attribute contributes
        * **Price**: 24/72 = 33.4%
        * **Meat**: 16/72 = 22.2%
        * **Guacamole**: 32/72 = 44.4%
        
### Interpreting Conjoint Importances

* Higher is more important
    * *Guac* is most important, followed by *Price*, then *Meat*
* Ratio scaled
    * Can say that *Guac* is twice as important as *Meat*
* Computing average importances
    * Compute for each respondent and then average
    
### Further Analysis

* If respondent characteristics are available, further analysis can be performed to understand relationships between characteristics and part-worths and importances
    * Correlation analysis between part-worths/importances and continuous respondent characteristics
    * Regression analysis with importances as the DV and characteristics as the IVs
    
### Prediction

* Can predict value of different profiles to see which is preferred
    * Can be done overall or on a case-by-case basis
    
## Traditional Conjoint Example

### Data

* Conjoint ratings from 40 people ($caseid$) on nine bundles
    * Value ($value$): (0 = Not at all; 100 = Very much)
    * Attributes:
        * $airline$
            * 1: Delta
            * 2: Spirit
            * 3: SW
        * $connect$
            * 1: None (No connections)
            * 2: One (One connection)
        * $price
            * 1: \$300
            * 2: \$450
            * 3: \$600
* Goal: Generate individual and average part-worths and importances

### Summarize

* Average value ratings by attribute levels

<caption>(\#tab:t08summ) Average Value Ratings by Attribute Levels ([R code](#table-reftabt08summ))</caption>

```{r t08summ, echo=FALSE}
airlineca %>% 
  group_by(airline) %>%
  summarise(mean=mean(value)) %>% flextable()

airlineca %>% 
  group_by(connect) %>%
  summarise(mean=mean(value)) %>% flextable()
  
airlineca %>% 
  group_by(price) %>%
  summarise(mean=mean(value)) %>% flextable()
```

### Regression results for one respondent

* For $caseid=13$

    ```{r echo=FALSE}
    aca13 <- airlineca %>% filter(caseid==13)
    
    lmaca13 <- lm(value~airline+connect+price, data=aca13)
    summary(lmaca13)$coefficients
    ```

* Part-Worth Utilities
    * Airline
        * SW = 13.33<br>Delta = 16.67<br>Spirit = 0
    * Connections
        * None = 5<br>One = 0
    * Price
        * \$300 = 81<br>\$450 = 47<br>\$600 = 0
        
### Importances for one respondent

* Sum of ranges:
    * $16.67+5+81=102.37$
* Airline Importance:
    * $\frac{16.67}{102.37}=16.28\%$
* Connections Importance:
    * $\frac{5}{102.37}=4.88\%$
* Price Importance:
    * $\frac{81}{102.37}=79.12\%$
    
### Average Part-Worth Utilities and Importances

``` {r t08avepw, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Part-Worth Plots ([R code](#figure-reffigt08avepw))"}
source("Topic08/tradca.R")
caform <- value ~ airline + connect + price
results <- tradca(formula=caform,
                  data=airlineca,
                  idvar="caseid")
results$pwplot
```
``` {r t08aveimp, echo=FALSE, fig.cap="Importance Plot ([R code](#figure-reffigt08aveimp))"}
results$impplot
```

### Explain Importances by Other Variables

<caption>(\#tab:t08expl) Explanation by Other Variables ([R code](#table-reftabt08expl))</caption>

``` {r t08expl, echo=FALSE, message=FALSE, warning=FALSE}
demos <- airlineca %>%
  group_by(caseid) %>%
  summarise(inc=first(inc),
            type=first(type)) %>%
  bind_cols(.,results$casetable[,2:12])

source("Topic08/cademo.R")
cademo(caform, demos, c("inc", "type"))
```

* $income$ has significant positive correlations with *Delta* and *SW* part-worths
* $income$ has a significant negative correlation with *\$300* price
* $income$ has a significant positive correlation with the importance of $airline$ and a significant negative correlation with the importance of $price$
* For a $\$1000$ increase in $income$, we would expect a $.33\%$ increase in the importance of $airline$
* For a $\$1000$ increase in $income$, we would expect a $.41\%$ decrease in the importance of $price$
* We would expect the importance of $price$ to be $14.5\%$ greater for *Pleasure* travelers than for *Business* travelers

### Predict Part-Worths for New Profiles

<caption>(\#tab:t08pred) Profile Predictions ([R code](#table-reftabt08expl))</caption>

```{r t08pred, echo=FALSE}
# Put your code for Q7 in this chunk
source("Topic08/capred.R")
prof1 <- c("airline_1", "connect_1", "price_2")
prof2 <- c("airline_2", "connect_1", "price_1")
capred(caform,results$casetable,prof1,prof2)
```

* On average, would prefer a cheaper flight on *Spirit* versus a more expensive flight on *Delta*
    * Although the difference is not significant ($95\%\text{ CIs}$ overlap)

## Suggested Readings

* *Multivariate Data Analysis*. Hair, Joseph F.; Black, William C.; Babin, Barry J.; Anderson, Rolph E.
    * 7th Edition: Search for “multivariate data analysis 7th edition hair”
        * Chapter 7: Conjoint Analysis
    * 5th Edition: Course reserves
        * Chapter 7: Conjoint Analysis
* Techincal papers on general conjoint analysis
    * [https://sawtoothsoftware.com/resources/technical-papers/categories/general-conjoint-analysis](https://sawtoothsoftware.com/resources/technical-papers/categories/general-conjoint-analysis)
        
## R Code

### Figure \@ref(fig:t08avepw) {.unlisted .unnumbered}

``` {r t08avepwcode, eval=FALSE}
source("Topic08/tradca.R")   # Load 'tradca.R' user-defined function
caform <- value ~ airline + connect + price   # Set formula
results <- tradca(formula=caform,  # Pass formula
                  data=airlineca,  # Pass data set
                  idvar="caseid")  # Pass ID variable
results$pwplot   # Request plot
```

### Figure \@ref(fig:t08aveimp) {.unlisted .unnumbered}

``` {r t08aveimpcode, eval=FALSE}
results$impplot  # Request importance plot from previous results
```

### Table \@ref(tab:t08summ) {.unlisted .unnumbered}

```{r t08summcode, eval=FALSE}
airlineca %>% 
  group_by(airline) %>%
  summarise(mean=mean(value))

airlineca %>% 
  group_by(connect) %>%
  summarise(mean=mean(value))
    
airlineca %>% 
  group_by(price) %>%
  summarise(mean=mean(value))
```

### Table \@ref(tab:t08expl) {.unlisted .unnumbered}

``` {r t08explcode, eval=FALSE}
# Create new dataframe with demographic variables attached to case-level
# part-worths and importances
demos <- airlineca %>%
  group_by(caseid) %>%
  summarise(inc=first(inc),
            type=first(type)) %>%
  bind_cols(.,results$casetable[,2:12])

source("Topic08/cademo.R")  # Load 'cademo.R' user defined function
cademo(caform,  # Pass formula
       demos,   # Pass demos dataframe
       c("inc", "type"))  # Provide demographic variable names
```


### Table \@ref(tab:t08pred) {.unlisted .unnumbered}

```{r t08predcode, eval=FALSE}
# Put your code for Q7 in this chunk
source("Topic08/capred.R")   # Load 'capred.R' user defined function
prof1 <- c("airline_1", "connect_1", "price_2")   # Set first profile
prof2 <- c("airline_2", "connect_1", "price_1")   # Set second profile
capred(caform,             # Pass formula
       results$casetable,  # Pass case-by-case part-worths and importances
       prof1,              # Pass profile 1
       prof2)              # Pass Profile 2
```