```{r echo=FALSE}
knitr::opts_chunk$set(comment=NA)
options(scipen=5)  # Turns off scientific notation
```

# Forecasting II

## R Packages and Datasets for Topic 10

``` {r t102packagesdata, message=FALSE}
library(ggplot2)       # Advanced graphing capabilities
library(dplyr)         # Easier programming
library(fpp3)
library(slider)
library(ggfortify)
load("Topic10/monthlysales.rdata")
```
``` {r, echo=FALSE}
library(flextable)
library(ggtext)
```

## Forecasting Methods

* Judgmental
    * Sales force estimates
    * Jury of experts
    * Structured processes
* Market/Product Analysis
    * Surveys
    * Market tests
    * ATAR
* Time Series
    * Naïve methods 
    * Smoothing techniques
    * Box-Jenkins methods
* Regression/Econometric
    * Linear
    * Non-Linear

## The Box-Jenkins Method

* An overall philosophy or method of identifying, fitting, and checking
* Provides adequate model for most any data pattern
* Appropriate for medium to long length (at least 50 observations)

### Stationary Time Series

* Box-Jenkins requires the time series to be stationary
    * Properties of the time series do not depend on the time at which the series is observed
* Why do we need the stationary assumption?
    * To make statements about autocorrelation 
    
    ```{r, echo=FALSE, cache=TRUE}
    load("Topic10/elecsales.rdata")
    source("Topic10/tsplot.R")
    tsplot(elecsales, "t", "sales", "ym", 0)
    ```

* What does this plot tell us?
    * Seasonality (12 months peak to peak)
    * Trend (increasing sales over time)
    * Heteroscedasticity (increasing variance over time)

### Autocorrelation

* Correlation is a measure of the linear relationship between two variables<br>
$\begin{aligned}
    r=\frac{\sum_{i=1}^{n}(x_i-\bar{x})\times (y_i-\bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}}
\end{aligned}$

* Autocorrelation is a measure of the linear relationship between lagged values of a time series<br>
$\begin{aligned}
    r_k=\frac{\sum_{t=k+1}^{T}(y_t-\bar{y})\times (y_{t-k}-\bar{y})}{\sum_{t=1}^{T}(y_t-\bar{y})^2}
\end{aligned}$
    * $r_1$ measures the relationship between $y_t$ and $y_{t-1}$
    * $r_2$ measures the relationship between $y_t$ and $y_{t-2}$
    
### Autocorrelation Function

* Autocorrelation used to determining the right model for the series
* Specifically, use the autocorrelation function
    * Graphs autocorrelation for successive lag values
    
    ```{r, echo=FALSE, cache=TRUE}
load("Topic10/germansales.rdata")
tsdata <- germansales %>%
  mutate(Date=yearquarter(t),
         Measure=sales) %>%
  as_tsibble(index=Date)
acfdata <- tsdata %>%
  ACF(difference(Measure, differences=1), lag_max=40)
acfdata %>%
  ggplot(aes(x=lag, y=acf)) +
  geom_segment(aes(xend=lag, yend=0), size=1, color="blue") +
  geom_point(aes(x=lag, y=acf), color="blue", size=2) +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(x="Lag", y="ACF")
    ```

### Partial Autocorrelation Function

* Partial autocorrelation can also be used to determining the right model for the series
* PACF removes the influence of intermediate lags
    * E.G., PACF of lag three is the correlation between $y_t$ and $y_{t-3}$ after removing the influence of $y_{t-1}$ and $y_{t-2}$

    ```{r, echo=FALSE, cache=TRUE}
pacfdata <- tsdata %>%
  PACF(difference(Measure, differences=1), lag_max=40)
pacfdata %>%
  ggplot(aes(x=lag, y=pacf)) +
  geom_segment(aes(xend=lag, yend=0), size=1, color="blue") +
  geom_point(aes(x=lag, y=pacf), color="blue", size=2) +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(x="Lag", y="PACF")
    ```   
    
### Forecasting ARMA

$AR(p)$:

* Autoregressive<br>Variable of interest is a linear combination of the past $p$ values of the variable<br>$y_t=c+\phi_1 y_{t-1}+\phi_2 y_{t-2}+\dots+\phi_p y_{t-p}+\varepsilon_t$
* A series displays “autoregressive” behavior if it tends to get pulled	back toward its mean.
* The larger the sum of the $AR$ coefficients, the more slowly the series returns to its mean.

$MA(q)$:

* Moving Average<br>Variable of interest is a weighted linear combination of the past $q$ forecast errors<br>$y_t=c+\varepsilon_t+\theta_1 \varepsilon_{t-1}+\theta_2 \varepsilon_{t-2}+\dots+\theta_q \varepsilon_{t-q}$
* A series displays “moving average” behavior if it seems to have random shocks felt in later periods.
* The $MA(q)$ coefficients represent the fraction of shock from $q$ periods ago that is still being felt.

$ARMA(p,q)$:

* $y_t=c+\phi_1 y_{t-1}+\dots+\phi_p y_{t-p}+\theta_1 \varepsilon_{t-1}+\dots+\theta_q \varepsilon_{t-q}\varepsilon_t+\varepsilon_t$

### Nonstationary Time Series

* Many time series exhibit nonstationary behavior
    * Box-Jenkins methodology is for stationary series…
    * Must make an adjustment before modeling
* Differencing
    * Can take care of nonstationarity
    * Instead of $y_t=\text{...}$<br>Use $y_t^\prime=\text{...}$<br>where $y_t^\prime=y_t - y_{t-1}$
    
    ```{r, echo=FALSE, warning=FALSE, cache=TRUE}
library(scales)
sdata <- tsdata %>% mutate(D.Sales=difference(Measure))

ggplot(sdata, aes(x=Date, y=Measure)) + 
   geom_line(aes(y=Measure), color="blue", size=1.5) +
   geom_line(aes(y=zmod), color="red", size=1.5,
             data=~transform(.,zmod=scales::rescale(D.Sales, 
                                                    range(Measure), 
                                                    range(D.Sales, na.rm=TRUE)))) +
   scale_x_yearquarter(date_breaks="3 years") +
   scale_y_continuous(sec.axis=sec_axis(~scales::rescale(., range(sdata$D.Sales, na.rm=TRUE), range(sdata$Measure)), name="Diff(Sales)")) +
   labs(y="Sales") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
    ```

### Forecasting ARIMA

$I(d)$:

* Integrated<br>Raw observations of the variable of interest are 	differenced $d$ times to make the series stationary

$ARMA(p,q)$
* $y_t=c+\phi_1 y_{t-1}+\dots+\phi_p y_{t-p}+\theta_1 \varepsilon_{t-1}+\dots+\theta_q \varepsilon_{t-q}\varepsilon_t+\varepsilon_t$

$ARIMA(p,d,q)$
* $y_t=c+\phi_1 y_{t-1}^\prime+\dots+\phi_p y_{t-p}^\prime +\theta_1 \varepsilon_{t-1}+\dots+\theta_q \varepsilon_{t-q}\varepsilon_t+\varepsilon_t$<br>where $y_t^\prime$ is the differenced series

### ARIMA with Seasonal Time Series

* Many time series exhibit seasonal fluctuations
    * Box-Jenkins methods can incorporate seasonality by including additional seasonal terms
* $ARIMA(p,d,q)$ becomes $ARIMA(p,d,q)(P,D,Q)_S$, where:
    * $(p,d,q)$ is the non-seasonal part of the model
    * $(P,D,Q)_S$ is the seasonal part of the model
        * $S$ is th enumber of observations per overall period
            * E.G., $S=12$ for monthly data, $S=4$ for quarterly data
* Differencing with seasonal data
    * Original Data

    ```{r, echo=FALSE, cache=TRUE, message=FALSE}
library(ggtext)
library(ggpubr)
edata <- elecsales %>%
  mutate(Date=yearmonth(t),
         Measure=lsales) %>% 
  as_tsibble(index=Date) %>%
  filter_index("1970-01"~"1980-01") %>%
  mutate(d.Measure=difference(Measure),
         dD12.Measure=difference(difference(Measure, lag=12), differences=1))

ggplot(edata, aes(x=Date, y=Measure)) + 
  geom_line(aes(y=Measure), color="blue", size=1.5) +
  labs(y="Sales")+
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 

ggplot(edata, aes(x=Date, y=Measure)) + 
  geom_line(aes(y=Measure), color="blue", size=1.5) +
  labs(y="Sales") +
  geom_segment(aes(x=yearmonth("1970 Jan"), y=25254.48, xend=yearmonth("1980 Jan"), yend=26989.62), color="orange", size=1) +
  geom_bracket(xmin=910, xmax=1290, y.position=26500, 
               size=2, color="red", label="", tip.length=c(0.13,0.06)) +
  geom_segment(aes(x=1100, y=26500, xend=1100, yend=26750), size=2, color="red") +
  geom_richtext(x=1100, y=26850, label="Clear Seasonality", label.color="NA",
                fill=NA, color="red", size=9) + 
  geom_richtext(x=2500, y=25250, label="Clear Trend", label.color="NA",
                fill=NA, color="red", size=9) +
  geom_segment(aes(x=2500, y=25350, xend=2400, yend=26375), 
                color="red", size=2, arrow=arrow())+
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 
    ```
    
    * Non-Seasonal Difference Data
    
    ```{r, echo=FALSE, warning=FALSE, cache=TRUE}

ggplot(edata, aes(x=Date, y=d.Measure)) + 
  geom_line(aes(y=d.Measure), color="blue", size=1.5) +
  labs(y="Sales (d = 1)") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 

ggplot(edata, aes(x=Date, y=d.Measure)) + 
  geom_line(aes(y=d.Measure), color="blue", size=1.5) +
  labs(y="Sales (d = 1)") +
  geom_bracket(xmin=1702, xmax=2065, y.position=-280, 
               size=2, color="red", label="", tip.length=c(-0.02,-0.05)) +
  geom_segment(aes(x=1883.5, y=-305, xend=1883.5, yend=-280), size=2, color="red") +
  geom_richtext(x=1883.5, y=-340, label="Clear Seasonality, but no Trend",
                label.color="NA", fill=NA, color="red", size=9)  +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 
    ```
    
    * Seasonal and Non-seasonal Differenced Data
    
    ```{r, echo=FALSE, warning=FALSE, cache=TRUE}

ggplot(edata, aes(x=Date, y=dD12.Measure)) + 
  geom_line(aes(y=dD12.Measure), color="blue", size=1.5) +
  labs(y="Sales (d = 1; D = 1") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 

ggplot(edata, aes(x=Date, y=dD12.Measure)) + 
  geom_line(aes(y=dD12.Measure), color="blue", size=1.5) +
  labs(y="Sales (d = 1; D = 1") +
  geom_richtext(x=1883.5, y=-200, label="No Trend or Seasonality",
                label.color="NA", fill=NA, color="red", size=9)  +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) 
    ```

## Box-Jenkins Method Overview

1. Identification<br>Using plots, ACFs, PACFs, and other information, a class of simple ARIMA models is selected
2. Estimation<br>Estimate the models using appropriate methods
3. Diagnostics<br>Check fitted models for inadequacies

### ARIMA

#### Model Identification

1. Start by identifying the order of differencing
    * If the ACF decays very slowly, it is likely a nonstationary series

    ``` {r, echo=FALSE, warning=FALSE, cache=TRUE}
source("Topic10/acplots.R")
load("Topic10/msales_noseas.rdata")
out <- acplots(msales.noseas, "t", "units", "ym", 0, 25, 0, 0)
out$acf
    ```

    * Try a first order differencing to make the series stationary
    * If autocorrelations die out quickly, the appropriate value of $d$ has been found

    ``` {r, echo=FALSE, warning=FALSE, cache=TRUE}
out <- acplots(msales.noseas, "t", "units", "ym", 0, 25, 1, 0)
out$acf
    ```

    * Be careful not to overdifference the series
2. Next, identify the $p$ and/or $q$ terms
    * For $p$: Use PACF
        * Identify how many significant lags before it “cuts off”
        * The last significant lag is the estimated value of $p$
            * In this example, two significant lags

    ``` {r, echo=FALSE, warning=FALSE, cache=TRUE}
out$pacf
    ```

    * For $p$: Run model with estimated $p$ term
        * Generate residuals from predicted values
        * Plot ACF and PACF residuals to see if significant auto-correlations still exist
        
    ``` {r, echo=FALSE, warning=FALSE, cache=TRUE}
    source("Topic10/autoarima.R")
    outarima <- autoarima(msales.noseas, "t", "units",
                          "ym", 12, c(2,1,0), c(0,0,0), "N")
    outarima$acresid
    ```

        * Use white noise test to see if the data come from a "white noise" process (i.e., uncorrelated with constant mean and variance)
            * $H_0$ is white noise

    ``` {r, echo=FALSE, warning=FALSE, message=FALSE}
    source("Topic10/tswh.noise.R")
    out <- tswh.noise(msales.noseas, "t", "units", "ym", 0, c(0,1,0), c(0,0,0))
    out + geom_richtext(x=.1, y=.93, label="ARIMA(0,1,0)", size=10, 
                color="darkorange", fill=NA, label.color=NA)

    out <- tswh.noise(msales.noseas, "t", "units", "ym", 0, c(2,1,0), c(0,0,0))
    out + geom_richtext(x=.1, y=.93, label="ARIMA(2,1,0)", size=10,
                        color="darkorange", fill=NA, label.color=NA)
    ```
    
    * For $q$: Use ACF  
        * If ACF has a sharp cutoff, consider the last lag before the cutoff for $q$  
        * If ACF has negative autocorrelation at lag 1, consider 1 for $q$  

    ``` {r, echo=FALSE, warning=FALSE, cache=TRUE}
    out <- acplots(msales.noseas, "t", "units", "ym", 0, 25, 1, 0)
    out$acf + geom_richtext(x=12, y=.275, label="ACF for d = 1", size=10, 
                color="darkorange", fill=NA, label.color=NA)

    out2 <- acplots(msales.noseas, "t", "units", "ym", 0, 25, 2, 0)
    out2$acf + geom_richtext(x=12, y=-.225, label="ACF for d = 2", size=10, 
                color="darkorange", fill=NA, label.color=NA)
    ```

    * In most cases, the best model is usually one with ONLY $AR$ terms or ONLY $MA$ terms
    * Mixed models (i.e., both $AR$ and $MA$ terms) may be the best fitting model, but caution should be used
        * E.g.; $ARIMA(2,1,0)$ vs. $ARIMA(2,2,1)$
        
#### Model Estimation

* Estimate model with maximum likelihood estimation 
    * Finds values of parameters that maximize probability of obtaining observed data
    * Similar to least squares by minimizing squared residuals
* Manual way to select final model
    * Run potential model using previous guidelines
    * Vary $p$ and $q$ from that model $\pm1$, and run models
    * Compare AIC values to see which is lowest
* Automatic selection
    * Many programs/packages have automatic searching procedures
    
#### Diagnostic Checking

* Once final model is selected, ensure that the autocorrelation plots of the residuals represent “white noise”
    * I.e., no further structure exists
* If further structure exists:
    * Check other potential models to eliminate the additional structure
* If further structure doesn't exist:
    * Check forecast accuracy on holdout periods
    
### Seasonal ARIMA

#### Model Identification

1. Start by identifying the order of differencing
    * If the data is clearly seasonal, examine the ACF plot from a first order seasonal difference, $D$
    * If the ACF shows a slow decay, try a first order difference also

    ```{r, echo=FALSE, warning=FALSE, cache=TRUE}
load("Topic10/autosales.rdata")
tsplot(autosales, "t", "units", "ym", 0)
out <- acplots(autosales, "t", "units", "ym", 0, 25, 0, 1)
out$acf
    ```

    * If autocorrelations die out quickly, the appropriate value of $d$ has been found

    ```{r, echo=FALSE, warning=FALSE, cache=TRUE}
out <- acplots(autosales, "t", "units", "ym", 0, 25, 1, 1)
out$acf
    ``` 

2. Identify the $P$ and/or $Q$ terms
    * Follow same general procedure as used for $p$ and $q$
        * If positive ACF of the differenced series at lag $s$, consider a $P$ term
            * More likely to occur if seasonal difference not used
        * If negative ACF of the differenced series at lag $s$, consider a $Q$ term
            * More likely to occur if seasonal difference is used
        * Try to avoid more than one or two seasonal parameters
            * E.g. $Q=2$ is two parameters, as is $P=1$ and $Q=1$

    ```{r, echo=FALSE, warning=FALSE}
    out <- acplots(autosales, "t", "units", "ym", 0, 25, 1, 1)
    out$acf + 
      geom_richtext(x=15, y=-.280, 
                    label="ACF for<br>ARIMA(0,1,0)(0,1,0)<sub>12</sub>",
                    size=10, 
                    color="darkorange", fill=NA, label.color=NA)
    out <- tswh.noise(autosales, "t", "units", "ym", 0, c(0,1,0), c(0,1,0))
    out + 
      geom_richtext(x=.15, y=.85, 
                    label="White Noise Test<br>ARIMA(0,1,0)(0,1,0)<sub>12</sub>",
                    size=10, 
                    color="darkorange", fill=NA, label.color=NA)
    out <- tswh.noise(autosales, "t", "units", "ym", 0, c(0,1,1), c(0,1,1))
    out + 
      geom_richtext(x=.15, y=.85, 
                    label="White Noise Test<br>ARIMA(0,1,1)(0,1,1)<sub>12</sub>",
                    size=10, 
                    color="darkorange", fill=NA, label.color=NA)
    ``` 

## ARIMA Forecasting Example 1

### Data

* Quarterly sales data from 1990 through 2012
* Variables:
    * Time period ($t$)
    * Sales from 1990 through 2010 ($sales$)
* Goal:  Forecast quarterly sales for the next two years

### Examine Data

```{r t102tsplot01, echo=FALSE, cache=TRUE, fig.cap="Time Series Plot ([R code](#figure-reffigt102tsplot01))"}
load("Topic10/qsales.rdata")    # Load Data
source("Topic10/tsplot.R")      # Source tsplot user defined function
tsplot(data=qsales,     # Data frame
       tvar="t",        # Date variable
       obs="sales",     # Measure variable
       datetype="yq",    # Date type
       h=8)             # Number of holdout periods
```

* Trend? *Yes*
* Seasonlity? *No*
* Models?
    * ARIMA
    
### Deterime $d$

* ACF of non-differenced sales shows very slow decay

    ```{r t102arima01, echo=FALSE, cache=TRUE, fig.cap="ACF of Non-Differenced Sales ([R code](#figure-reffigt102arima01))"}
source("Topic10/acplots.R")    # Source acplots user defined function
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=0,             # No differencing
        D=0)$acf         # No seasonal differencing; request ACF plot
    ```

* Try $d=1$
* ACF of first-differenced sales shows no significant lags early on
    * Use $d=1$ in modeling

    ```{r t102arima02, echo=FALSE, cache=TRUE, fig.cap="ACF of First-Order Differenced Sales ([R code](#figure-reffigt102arima02))"}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
    ```

    
### Determine $p$

* PACF of first-differenced sales shows some significant lags, but appear random
    * $p=0$ probably appropriate

    ```{r t102arima03, echo=FALSE, cache=TRUE, fig.cap="PACF of First=Order Differenced Sales ([R code](#figure-reffigt102arima03))"}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$pacf         # No seasonal differencing; request PACF plot
    ```

### Determine $q$

* ACF of first-differenced sales shows:
    * No sharp cutoff
    * No significant negative correlation at lag 1
* $q=0$ probably appropriate

    ```{r t102arima04, echo=FALSE, cache=TRUE, fig.cap="ACF of First-Order Differenced Sales ([R code](#figure-reffigt102arima04))"}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
    ```

### Check White Noise

* Run Model $ARIMA(0,1,0)$ and check white noise test
    * Test results suggest model would be appropriate

```{r t102arima05, echo=FALSE, fig.cap="White Noise Test for ARIMA(0,1,0) ([R code](#figure-reffigt102arima05))"}
source("Topic10/tswh.noise.R")
tswh.noise(data=qsales,     # Data frame
           tvar="t",        # Date variable
           obs="sales",     # Measure variable
           datetype = "yq", # Date type quarterly
           h=8,             # Number of holdout periods
           c(0,1,0),        # ARIMA terms (p,d,q) 
           c(0,0,0))        # SARIMA terms (P,D,Q)
```

### Model Selection

* Use $ARIMA(0,1,0)$ as "starting" model
* Use automatic selection algorithm to fine "best" model
* Model automatically selected — $ARIMA(1,1,2)$ — is considerably better than "starting model"
    * Lower forecast accuracy measures and lower AIC
    
<caption>(\#tab:t102arima06) ARIMA Model Accuracy ([R code](#table-reftabt102arima06))</caption>
    
```{r t102arima06, echo=FALSE, cache=TRUE}
source("Topic10/autoarima.R")
# Save results to object called 'arima'
arima <- autoarima(data=qsales,     # Data frame
                   tvar="t",        # Date variable
                   obs="sales",     # Measure variable
                   datetype = "yq", # Date type quarterly
                   h=8,             # Number of holdout periods
                   c(0,1,0),        # ARIMA terms (p,d,q) 
                   c(0,0,0),        # SARIMA terms (P,D,Q)
                   auto="Y")        # Request automatic search
flextable(arima$acc)   # Request accuracy table
```

* Check diagnostics for $ARIMA(1,1,2)$ (i.e., "Auto")
    * ACF and PACF look good with no worrisome significant correlations
    * White noise test looks good

    ```{r t102arima07, echo=FALSE, cache=TRUE, fig.cap="ACF/PACF of Model Residuals ([R code](#figure-reffigt102arima07))"}
arima$acresid
    ```
    ```{r t102arima08, echo=FALSE, cache=TRUE, fig.cap="White Noise Test of Models ([R code](#figure-reffigt102arima08))"}
arima$wn
    ```

### Model Forecast

* Use dynamic forecast for $ARIMA(1,1,2)$
* Compare with Holt-Winters Additive
* Holt-Winters Additive predicting better

<caption>(\#tab:t102arima09) ARIMA Forecast Residual Comparison with Holt-Winters Additive ([R code](#table-reftabt102arima09))</caption>

```{r t102arima09, echo=FALSE, cache=TRUE}
source("Topic10/smoothfc.R")
smooth <- smoothfc(qsales, "t", "sales", "yq", 8)
results <- list(arima, smooth)
models <- c("Auto", "H-W.Add")
source("Topic10/fccompare.R")
compare <- fccompare(results, models)
flextable(compare$acc)
```
```{r t102arima10, echo=FALSE, cache=TRUE, fig.cap="ARIMA Forecast Comparison with Holt-Winters Additive ([R code](#figure-reffigt102arima10))"}
compare$fcresplot
```

## ARIMA Forecasting Example 2

### Data

* Monthly Sales from 2005 through 2016
* Variables:
    * Time period ($t$)
    * Sales per period ($sales$)
* Goal:  Forecast quarterly sales for the next 12 months

### Examine Data

```{r t102tsplot03, echo=FALSE, fig.cap="Time Series Plot ([R code](#figure-reffigt102tsplot03))"}
load("Topic10/msales.rdata")    # Load Data
tsplot(data=msales,     # Data frame
       tvar="t",        # Date variable
       obs="sales",     # Measure variable
       datetype="ym",    # Date type
       h=12)             # Number of holdout periods
```

* Trend? *Yes*
* Seasonlity? *Yes*
* Models?
    * Seasonal ARIMA
    
### Deterime $d$ and $D$

* ACF of non-differenced sales shows very slow decay
    * Try $d=1$
* Wave pattern suggest seasonality

    ```{r t102sarima01, echo=FALSE, cache=TRUE, fig.cap="ACF of Non-Differenced Sales ([R code](#figure-reffigt102sarima01))"}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=0,             # No differencing
        D=0)$acf         # No seasonal differencing; request ACF plot
    ```

* Try $d=1$
* ACF of first-differenced sales still shows significant correlations at intervals of 12 lags
    * Try $D=1$

    ```{r t102sarima02, echo=FALSE, cache=TRUE, fig.cap="ACF of First-Order Non-Seasonal Differenced Sales ([R code](#figure-reffigt102sarima02))"}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
    ```

* ACF of first-differenced non-seasonal and seasonal sales
    * Sharp cutoff suggests trend and seasonality accounted for

    ```{r t102sarima022, echo=FALSE, cache=TRUE, fig.cap="ACF of First-Order Non Seasonal and Seasonal Differenced Sales ([R code](#figure-reffigt102sarima022))"}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$acf         # No seasonal differencing; request ACF plot
    ```


### Determine $p$

* PACF of differenced sales shows cutoff afer 1 lag
    * Begin with $p=1$

    ```{r t102sarima03, echo=FALSE, cache=TRUE, fig.cap="PACF of Differenced Sales ([R code](#figure-reffigt102sarima03))"}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$pacf         # No seasonal differencing; request PACF plot
    ```

### Determine $q$

* ACF of differenced sales shows negative correlation at first lag
    * Begin with $q=1$

    ```{r t102sarima04, echo=FALSE, cache=TRUE, fig.cap="ACF of Differenced Sales ([R code](#figure-reffigt102sarima04))"}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$acf         # No seasonal differencing; request ACF plot
    ```

### Determine $P$ and $Q$

* ACF of differenced sales shows negative correlation at lage $s$
    * Begin with $Q=1$
    * No $P$ term

### Check White Noise

* Run Model $ARIMA(1,1,1)(0,1,1)_{12}$ and check white noise test
    * Test results suggest model would be appropriate

```{r t102sarima05, echo=FALSE, fig.cap="White Noise Test for ARIMA(1,1,1)(0,1,1)12 ([R code](#figure-reffigt102sarima05))"}
tswh.noise(data=msales,     # Data frame
           tvar="t",        # Date variable
           obs="sales",     # Measure variable
           datetype = "ym", # Date type quarterly
           h=12,            # Number of holdout periods
           c(1,1,1),        # ARIMA terms (p,d,q) 
           c(0,1,1))        # SARIMA terms (P,D,Q)
```

### Model Selection

* Use $ARIMA(1,1,1)(0,1,1)_{12}$ as "starting" model
* Use automatic selection algorithm to fine "best" model
* Model automatically selected — $ARIMA(1,0,1)(0,1,1)_{12})$ — is not better than the starting model
    * Two models measures are fairly equal
    
<caption>(\#tab:t102sarima06) ARIMA Model Accuracy ([R code](#table-reftabt102sarima06))</caption>
    
```{r t102sarima06, echo=FALSE, cache=TRUE}
# Save results to object called 'sarima'
sarima <- autoarima(data=msales,     # Data frame
                   tvar="t",        # Date variable
                   obs="sales",     # Measure variable
                   datetype = "ym", # Date type quarterly
                   h=12,            # Number of holdout periods
                   c(1,1,1),        # ARIMA terms (p,d,q) 
                   c(0,1,1),        # SARIMA terms (P,D,Q)
                   auto="Y")        # Request automatic search
flextable(sarima$acc)   # Request accuracy table
```

* Check diagnostics for both models$ARIMA(1,1,2)$ (i.e., "Auto")
    * ACF and PACF look good for both models
    * White noise test looks good for both models

    ```{r t102sarima07, echo=FALSE, cache=TRUE, fig.cap="ACF/PACF of Model Residuals ([R code](#figure-reffigt102sarima07))"}
sarima$acresid
    ```
    ```{r t102sarima08, echo=FALSE, cache=TRUE, fig.cap="White Noise Test of Models ([R code](#figure-reffigt102sarima08))"}
sarima$wn
    ```

### Model Forecast

* Use dynamic forecast for both models
* Compare with Linear Regression with Seasonal Trend
* All three models perform about the same

<caption>(\#tab:t102sarima09) ARIMA Forecast Residual Comparison with Linear Regression Seasonal Trend ([R code](#table-reftabt102sarima09))</caption>

```{r t102sarima09, echo=FALSE, cache=TRUE}
source("Topic10/linregfc.R")
linreg <- linregfc(msales, "t", "sales", "ym", 12)
results <- list(sarima, linreg)
models <- c("Auto", "Self", "Lin.Reg.Seas.Trend")
compare <- fccompare(results, models)
flextable(compare$acc)
```
```{r t102sarima10, echo=FALSE, cache=TRUE, fig.cap="ARIMA Forecast Comparison with Linear Regression Seasonal Trend ([R code](#figure-reffigt102sarima10))"}
compare$fcresplot
```


## Suggested Readings

* *Principles of Marketing Engineering and Analytics, 3rd Edition* (2017). Lilien, Gary L., Rangaswamy, Arvind, and De Bruyn, Arnaud.
    * Course reserves
        * Chapter 5: Forecasting
* *Forecasting: Principles and Practice, 3rd Edition* (2021). Hyndman, Rob J., and Athanasopoulos, George.
    * Online Texts<br><a href="https://otexts.com/fpp3/" target="_blank" rel="noopener noreferrer">https://otexts.com/fpp3/</a>
        
## R Code

### Figure \@ref(fig:t102tsplot01) {.unlisted .unnumbered}

```{r t102tsplot01code, eval=FALSE}
load("qsales.rdata")    # Load Data
source("tsplot.R")      # Source tsplot user defined function
tsplot(data=qsales,     # Data frame
       tvar="t",        # Date variable
       obs="sales",     # Measure variable
       datetype="yq",   # Date type
       h=8)             # Number of holdout periods
```

### Figure \@ref(fig:t102arima01) {.unlisted .unnumbered}

```{r t102arima01code, eval=FALSE}
source("acplots.R")      # Source acplots user defined function
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=0,             # No differencing
        D=0)$acf         # No seasonal differencing; request ACF plot
```

### Figure \@ref(fig:t102arima02) {.unlisted .unnumbered}

```{r t102arima02code, eval=FALSE}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
```

### Figure \@ref(fig:t102arima03) {.unlisted .unnumbered}

```{r t102arima03code, eval=FALSE}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$pacf         # No seasonal differencing; request PACF plot
```

### Figure \@ref(fig:t102arima04) {.unlisted .unnumbered}

```{r t102arima04code, eval=FALSE}
acplots(data=qsales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "yq", # Date type quarterly
        h=8,             # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
```

### Figure \@ref(fig:t102arima05) {.unlisted .unnumbered}

```{r t102arima05code, eval=FALSE}
source("tswh.noise.R")
tswh.noise(data=qsales,     # Data frame
           tvar="t",        # Date variable
           obs="sales",     # Measure variable
           datetype = "yq", # Date type quarterly
           h=8,             # Number of holdout periods
           c(0,1,0),        # ARIMA terms (p,d,q) 
           c(0,0,0))        # SARIMA terms (P,D,Q)
```

### Figure \@ref(fig:t102arima07) {.unlisted .unnumbered}

```{r t102arima07code, eval=FALSE}
arima$acresid
```

### Figure \@ref(fig:t102arima08) {.unlisted .unnumbered}

```{r t102arima08code, eval=FALSE}
arima$wn
```

### Figure \@ref(fig:t102arima10) {.unlisted .unnumbered}

```{r t102arima10code, eval=FALSE}
compare$fcresplot
```

### Figure \@ref(fig:t102tsplot03) {.unlisted .unnumbered}

```{r t102tsplot03code, eval=FALSE}
load("msales.rdata")    # Load Data
tsplot(data=msales,     # Data frame
       tvar="t",        # Date variable
       obs="sales",     # Measure variable
       datetype="ym",   # Date type
       h=12)            # Number of holdout periods
```


### Figure \@ref(fig:t102sarima01) {.unlisted .unnumbered}

```{r t102sarima01code, eval=FALSE}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=0,             # No differencing
        D=0)$acf         # No seasonal differencing; request ACF plot
```


### Figure \@ref(fig:t102sarima02) {.unlisted .unnumbered}

```{r t102sarima02code, eval=FALSE}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=0)$acf         # No seasonal differencing; request ACF plot
```


### Figure \@ref(fig:t102sarima022) {.unlisted .unnumbered}

```{r t102sarima022code, eval=FALSE}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$acf         # 1st order seasonal differencing; request ACF plot
```


### Figure \@ref(fig:t102sarima03) {.unlisted .unnumbered}

```{r t102sarima03code, eval=FALSE}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$pacf        # 1st order seasonal differencing; request PACF plot
```

### Figure \@ref(fig:t102sarima04) {.unlisted .unnumbered}

```{r t102sarima04code, eval=FALSE}
acplots(data=msales,     # Data frame
        tvar="t",        # Date variable
        obs="sales",     # Measure variable
        datetype = "ym", # Date type quarterly
        h=12,            # Number of holdout periods
        lags=25,         # Number of lags to show
        d=1,             # 1st order difference
        D=1)$acf         # 1st order seasonal differencing; request ACF plot
```

### Figure \@ref(fig:t102sarima05) {.unlisted .unnumbered}

```{r t102sarima05code, eval=FALSE}
tswh.noise(data=msales,     # Data frame
           tvar="t",        # Date variable
           obs="sales",     # Measure variable
           datetype = "ym", # Date type quarterly
           h=12,            # Number of holdout periods
           c(1,1,1),        # ARIMA terms (p,d,q) 
           c(0,1,1))        # SARIMA terms (P,D,Q)
```

### Figure \@ref(fig:t102sarima07) {.unlisted .unnumbered}

```{r t102sarima07code, eval=FALSE}
sarima$acresid
```

### Figure \@ref(fig:t102sarima08) {.unlisted .unnumbered}

```{r t102sarima08code, eval=FALSE}
sarima$wn
```

### Figure \@ref(fig:t102sarima10) {.unlisted .unnumbered}

```{r t102sarima10code, eval=FALSE}
compare$fcresplot
```

### Table \@ref(tab:t102arima06) {.unlisted .unnumbered}

```{r t102arima06code, eval=FALSE}
source("autoarima.R")
# Save results to object called 'arima'
arima <- autoarima(data=qsales,     # Data frame
                   tvar="t",        # Date variable
                   obs="sales",     # Measure variable
                   datetype = "yq", # Date type quarterly
                   h=8,             # Number of holdout periods
                   c(0,1,0),        # ARIMA terms (p,d,q) 
                   c(0,0,0),        # SARIMA terms (P,D,Q)
                   auto="Y")        # Request automatic search
arima$acc   # Request accuracy table
```

### Table \@ref(tab:t102arima09) {.unlisted .unnumbered}

```{r t102arima09code, eval=FALSE}
source("smoothfc.R")
smooth <- smoothfc(qsales, "t", "sales", "yq", 8)
results <- list(arima, smooth)
models <- c("Auto", "H-W.Add")
source("fccompare.R")
compare <- fccompare(results, models)
compare$acc
```

### Table \@ref(tab:t102sarima06) {.unlisted .unnumbered}

```{r t102sarima06code, eval=FALSE}
# Save results to object called 'sarima'
sarima <- autoarima(data=msales,     # Data frame
                   tvar="t",        # Date variable
                   obs="sales",     # Measure variable
                   datetype = "ym", # Date type quarterly
                   h=12,            # Number of holdout periods
                   c(1,1,1),        # ARIMA terms (p,d,q) 
                   c(0,1,1),        # SARIMA terms (P,D,Q)
                   auto="Y")        # Request automatic search
sarima$acc   # Request accuracy table
```

### Table \@ref(tab:t102sarima09) {.unlisted .unnumbered}

```{r t102sarima09code, eval=FALSE}
source("linregfc.R")
linreg <- linregfc(msales, "t", "sales", "ym", 12)
results <- list(sarima, linreg)
models <- c("Auto", "Self", "Lin.Reg.Seas.Trend")
compare <- fccompare(results, models)
compare$acc
```